\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{helvet}

\renewcommand{\familydefault}{\sfdefault}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE Yang Cai}\\
    \vspace{0.1cm}
    Ningbo, China \\
    Email: seewhysimon@mail.nwpu.edu.cn \\
    Phone: +86-188-5741-9883 \\
    GitHub: https://github.com/SeeWhysimon
\end{center}

\section*{Education}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Northwestern Polytechnical University, Xi'an, China} \hfill \textit{Sept. 2022 -- Present} \\
    \textit{Bachelor, Information Engineering} \\
    GPA: 3.65/4.1, 88.72/100 \\
    Relevant Courses: Calculus H, Course 2, Course 3, Course 4
\end{itemize}

\section*{Research Experience}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Co-Principal Investigator, National-Level College Student Innovation and Entrepreneurship Project on Hybrid Engine Design} \\
    \textit{Northwestern Polytechnical University, Xi'an, China} \hfill \textit{April 2024 -- Present} 
    
    \begin{itemize}
        \item Supervised by Professor Yongqiang Shi.
        \item Co-led the design and implementation of an algorithm based on automatic control principles and machine learning, enabling the engine to autonomously adjust its speed.
        \item Oversaw the deployment of the algorithm onto hardware, facilitating long-distance travel by leveraging hybrid power from both fuel and electricity.
    \end{itemize}
    
\end{itemize}

\section*{Internship Experience}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Position, Company/Institution Name, Location} \hfill \textit{Month Year -- Month Year} 
    
    \begin{itemize}
        \item Brief description of your responsibilities and achievements.
        \item Another significant achievement or task.
    \end{itemize}
    
    \item \textbf{Position, Company/Institution Name, Location} \hfill \textit{Month Year -- Month Year}
    
    \begin{itemize}
        \item Brief description of your responsibilities and achievements.
        \item Another significant achievement or task.
    \end{itemize}
\end{itemize}

\section*{Competition Experience}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Mathematical Contest in Modeling (MCM)} \hfill \textit{January 2024} \\
    \textit{Honorable Mention} \\
    Participated in the Mathematical Contest in Modeling (MCM), 
    a prestigious international competition that challenges students to solve real-world problems using mathematical modeling. 
    My team worked on a problem related to the control of water flow in the Great Lakes, developed a robust model, and provided innovative solutions, 
    leading to the achievement of the Honorable Mention.
\end{itemize}

\section*{Honors \& Awards}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Second-Class Scholarship}, \textit{Northwestern Polytechnical University} \hfill \textit{December 2023} \\
    Awarded for outstanding academic performance in the academic year 2022-2023, recognizing consistent excellence in coursework and overall academic achievements.

    \item \textbf{Diligent Study Model}, \textit{Northwestern Polytechnical University} \hfill \textit{December 2023} \\
    Recognized as an exemplary individual for dedication and perseverance in studies, awarded to students who demonstrate exceptional commitment to academic growth.
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Programming Languages:} C (Proficient), Python (Proficient)
    \item \textbf{Tools \& Technologies:} MATLAB, LaTeX (Proficient)
\end{itemize}

\section*{Languages}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Chinese:} Native
    \item \textbf{English:} Proficient
\end{itemize}

\section*{Extracurricular Achievements}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Yan Yiti Cup}, \textit{Northwestern Polytechnical University} \hfill \textit{November 2023} 
    \begin{itemize}
        \item 4th Place in Men's 50m Freestyle
        \item 1st Place in Men's 50m Backstroke
        \item 1st Place in Men's 4x50m Relay
        \item 1st Place in Mixed 4x50m Relay
    \end{itemize}
\end{itemize}


\end{document}
